---
title: "Advanced Bioinformatics 2019 assessment"
author: "m1606654"
date: "10/04/2020"
output: rmarkdown: github_document
---


Task 3.1
```{r}
sum(5:55) 
```

Task 3.2
#ASSIGNS sumfun as a function that takes n as an imput but always calculates the sim of all integers between 5 and n)
```{r}
sumfun <- function(n) {sum(5:n)}
sumfun(10)
sumfun(20)
sumfun(100)
```

Task 3.3
#This states that n is equal to 12 and that our desired length for the fibonnaci sequence is equal to n
#Then we can use a for-loop to add one to the first element of x, add two to the second element of x and so on. We use the variable n to store the number of elements in x. In the loop, we will use the variable x to loop through the first 12 numbers.
# This for-loop creates a vector with 12 components where each component is added to the previous one

```{r}
n <- 12
fibonacci <- numeric(n)
fibonacci[1] <- 1
fibonacci[2] <- 1
for (x in 3:n)
{fibonacci[x] <- fibonacci[x-1]+fibonacci[x-2]} 

fibonacci

```

Task 3.4
```{r}
library(ggplot2)
ggplot(data=mtcars,aes(x=as.factor(gear),y=mpg)) + geom_boxplot(aes(col=as.factor(gear)))


```

Task 3.5
Fitted slope: 3.9342 Std. Error = 0.4155
Intercept: -17.5791 Std. Error = 6.7584
Variables: Speed: (mph) 
Distance: (feet) 

```{r}
linearMod <- lm(dist ~ speed, data = cars)
summary(linearMod)

```

Task 3.6
```{r}
library(ggplot2)
ggplot(cars,aes(speed,dist))+ geom_point() + geom_smooth(method="lm",formula="y~x") + labs(x="Speed (mph)",y="Stopping Distance (feet)")
```

Task3.7
First create a model whereby braking distance is proportional to velocity squared.
Then use summary to find the residuals (differences between observed points and predicted points).
Find the average of the residuals
Calculate reaction time
Plot the reaction time model
```{r}
reaction_time_model <- lm(dist ~ I(speed^2)+0, data = cars)
summary(reaction_time_model)
resdata <- reaction_time_model$residuals
print(resdata)
mean(resdata)


library(ggplot2)
ggplot(cars,aes(speed,dist))+geom_point()+geom_smooth(method="lm",formula = "y~I(x^2)+0")

```

